---
title: "Qualitative Network Modeling in QPress"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

options(figure_counter = TRUE)

```

```{r Fig counter setup}

# http://rmflight.github.io/post/writing-papers-using-r-markdown/


# Create variable that stores number, adds incremental value

incCount <- function(inObj){
    nObj <- length(inObj)
    useNum <- max(inObj) + 1
    inObj <- c(inObj, useNum)
    inObj
}

figCount <- 0
tableCount <- 0

# Insert variable with named number into text

pasteLabel <- function(preText, inObj, objName, insLink=TRUE){
    objNum <- tail(inObj, n = 1)
    
    useText <- paste(preText, objNum, sep=" ")
    if (insLink){
        useText <- paste("[", useText, "](#", objName, ")", sep="")
    }
    useText
}

```

```{r Load libraries}
########################################################################
# All code was originally obtained from  Melbourne-Thomas et al. 2012. #
# Modified by Jon Reum and Jesse Coleman                               #
########################################################################

# In case QPress needs to be reinstalled:
# devtools::install_github("SWotherspoon/QPress")

library("QPress", lib.loc="/Library/Frameworks/R.framework/Versions/3.5/Resources/library")
require(dplyr)
require(purrr)
require(tidyr)
require(ggplot2)
require(reshape2)
require(ggmap)
require(stringr)
require(DiagrammeR)
require(DiagrammeRsvg)
require(rsvg)
require(leaflet)
require(sp)
```

```{r Modify QPress functions}

# Alternative adjacency image function

adjacency.image2 = function(edges, modelname) {
  ggplot(edges %>% complete(From, nesting(To), fill = list(Type = "Z")), 
            aes(y = rev(To), x = From, fill = Type)) +
  geom_tile(color = "white") +
  scale_fill_manual(values = c("#81B8D6", "#EF936F", "808080"), 
                    name = "Interaction", 
                    labels = c("Neg", "Pos", "Zero")) +
  theme_minimal() + 
  labs(y = "", x = paste(modelname)) +
  scale_y_discrete(expand = c(0, 0), labels = rev(levels(edges$From))) +
  scale_x_discrete(position = "top", expand = c(0, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0), 
        axis.ticks = element_blank())
  
}

environment(adjacency.image2) <- as.environment(".GlobalEnv")

# Heat table function

heatimptable <- function(imptable) {
  ggplot(melt(imptable), aes(Var2, Var1, fill = value)) +
    geom_tile(color = "white") +
    scale_fill_gradient2(low = "#81B8D6", high = "#EF936F", mid = "808080", 
                         midpoint = 0, limit = c(-1,1), space = "Lab", guide = FALSE) +
    geom_text(aes(Var2, Var1, label = round(value, 2)), color = "black", size = 2) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, size = 8, hjust = 1),
      axis.text.y = element_text(size = 8),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.grid.major = element_blank(),
      panel.border = element_blank(),
      panel.background = element_blank(),
      axis.ticks = element_blank(),
      legend.justification = c(1, 0),
      legend.position = c(0.6, 0.7),
      legend.direction = "horizontal")
  
}

environment(heatimptable) <- as.environment(".GlobalEnv")


# Utility function

extend.vector <- function(named,nodes,default) {
  if(is.null(names(named)))
    v <- rep(named,length.out=length(nodes))
  else {
    k <- match(names(named),nodes)
    if(any(is.na(k)))
      warning("Unknown nodes:",paste(names(named)[is.na(k)],collapse=" "))
    v <- rep(default,length(nodes))
    v[k] <- named
  }
  v
}

environment(extend.vector) <- as.environment(".GlobalEnv")

# Modify impact.barplot0 to include 'cex.names' argument for adjusting edge label text size.

impact.barplot2 <- function (sim, perturb = 0, monitor = NA, epsilon = 1e-05, main = "", 
    cex.axis = 0.75, cex.names = 0.75) 
{
    As <- sim$A
    nodes <- node.labels(sim$edges)
    pal <- c("#92C5DE", "#808080", "#F4A582")
    results <- matrix(0, length(nodes), 3)
    perturb <- extend.vector(perturb, nodes, 0)
    monitor <- extend.vector(monitor, nodes, NA)
    for (i in seq_along(As)) {
        impact <- signum(drop(As[[i]] %*% perturb), epsilon = epsilon)
        if (all(monitor == impact, na.rm = T)) {
            results <- results + outer(impact, -1:1, "==")
        }
    }
    rownames(results) <- nodes
    lwidth <- max(strwidth(nodes, units = "inches", cex = cex.axis))
    opar <- par(mai = c(1, lwidth + 0.2, 0.4, 0.4) + 0.2)
    barplot(t(results), horiz = T, las = 1, border = F, col = pal, 
        xlab = "Simulations", main = main, cex.axis = cex.axis, cex.names = cex.names)
    par(opar)
}

environment(impact.barplot2) <- as.environment(".GlobalEnv")

```

```{r Digraph function}
# Function to create simple digraph

make_digraph <- function(edges.model.name) {

nodes <- create_node_df(n = length(levels(edges.model.name$From)),
                        label = levels(edges.model.name$From),
                        shape = "rectangle",
                        fontname = "Helvetica"
                        )

pos <- create_edge_df(
  from = edges.model.name$From[edges.model.name$Type == "P"],
  to = edges.model.name$To[edges.model.name$Type == "P"],
  arrowhead = "normal",
  color = "grey")

neg <- create_edge_df(
  from = edges.model.name$From[edges.model.name$Type == "N"],
  to = edges.model.name$To[edges.model.name$Type == "N"],
  arrowhead = "dot",
  color = "grey")

all_edges <- combine_edfs(pos, neg)

graph <- create_graph(
    nodes_df = nodes,
    edges_df = all_edges,
    attr_theme = NULL,
    directed = TRUE
    )

return(graph)

}

```

# Methods

## Study Communities

```{r Map, out.width = '1000px', out.height = '800px', eval = FALSE}
# Enter list of communities and lats/longs

cdqs <- read.csv("/Volumes/GoogleDrive/My Drive/GIS/AK/AK_Places/CDQ_Communities_LatLong.csv", header = TRUE)

cdqs[18,c(5,6)] <- c(-164.8435, 62.53281)
cdqs[30,c(5,6)] <- c(-165.1047, 60.52948)

cdqs <- cdqs %>% add_row(X = 999, Community = "Unalaska/Dutch Harbor", CDQ_Group = "Aleutian Pribilof Islands Community Development Association", CDQ_Acro = "APICDA", Longitude = -166.5346, Latitude = 53.87245) %>%
  rename(lat = Latitude, lon = Longitude)

study_coms <- data.frame(Community = c("Mekoryuk", "Saint Paul", "Savoonga", "Unalaska/Dutch Harbor"), lon = c(-166.1872, -170.2782, -170.4834, -166.5346), lat = c(60.38723, 57.12114, 63.68954, 53.87245))

leaflet(options = leafletOptions(minZoom = 0, maxZoom = 18))
leaflet(study_coms) %>% 
  addTiles() %>% 
  addMarkers(label = ~Community,
             labelOptions = labelOptions(noHide = TRUE))
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Map of study communities.

# Results

```{r Map QPress over all models, fig.show = 'hide'}

# Create list of path names to Dia models
path <- c("/Volumes/GoogleDrive/My Drive/Halibut Paradigm/Edge Lists/")

edge_paths <- list(stpaul = paste(path, "stpaul.txt", sep = ""), 
                  savoonga = paste(path, "savoonga.txt", sep = ""),
                  unalaska = paste(path, "unalaska.txt", sep = ""),
                  am80 = paste(path, "am80.txt", sep = ""),
                  mekoryuk_b = paste(path, "mekoryuk_before.txt", sep = ""),
                  mekoryuk_b_linked = paste(path, "mekoryuk_before_linked.txt", sep = ""),
                  mekoryuk_a = paste(path, "mekoryuk_after.txt", sep = ""))

model_names <- c("St. Paul", "Savoonga", "Unalaska/Dutch Harbor", "Amendment 80", "Mekoryuk Before", "Mekoryuk Before linked","Mekoryuk After")


# Convert edge lists to data frame for use in QPress simulations

edges <- edge_paths %>% map(~ read.digraph(.))


# Make digraph objects for later rendering

digraphs <- edges %>% map(~ make_digraph(.))


# Make all subgraphs (each node and its neighbors)

# subdigraphs <- edges %>% map(~ create_all_subgraphs(.))


# Add self-limitation of each node (i.e., -1 on the diagonal of the community matrix)

edges_lim <- edges %>% map(~ enforce.limitation(.))


# Build adjacency (community) matrices for all models

adj_mats <- edges_lim %>% map(~ adjacency.matrix(labels = TRUE, edges = .))


# Produce plot of adjacency matrices (effect of column node on row node) with light blue for negative and orange for positive interactions.

adj_images <- map2(.x = edges_lim, .y = model_names, .f = adjacency.image2)


# Run simulations
# Not working...in progress

# argslist <-list(
#   n.sims <- c(rep(1000, 4)),
#   edges <- edges_lim,
#   required.groups <- c(rep(c(0))),
#   sampler <- community.sampler(edges_lim),
#   validators <- c(rep(NULL, 4))
# )


# Need pmap for multiple arg lists, and invoke_map for multiple functions taken as arguments
# sims <<- pmap(.l = argslist, .f = system.simulate)
             
# The Old Fashioned way

sims <- list(
  stpaul = system.simulate(n.sims = 1000, edges = edges_lim$stpaul, sampler = community.sampler(edges_lim$stpaul), validators = NULL),
  savoonga = system.simulate(n.sims = 1000, edges = edges_lim$savoonga, sampler = community.sampler(edges_lim$savoonga), validators = NULL),
  unalaska = system.simulate(n.sims = 1000, edges = edges_lim$unalaska, sampler = community.sampler(edges_lim$unalaska), validators = NULL),
  am80 = system.simulate(n.sims = 1000, edges = edges_lim$am80, sampler = community.sampler(edges_lim$am80), validators = NULL),
  mekoryuk_b = system.simulate(n.sims = 1000, edges = edges_lim$mekoryuk_b, sampler = community.sampler(edges_lim$mekoryuk_b), validators = NULL),
  mekoryuk_a = system.simulate(n.sims = 1000, edges = edges_lim$mekoryuk_a, sampler = community.sampler(edges_lim$mekoryuk_a), validators = NULL))

```

```{r Modify interaction strengths, eval = FALSE}

# As a test, I am weakening the effect of Value of groundfish CDQ on CBSFA in the St. Paul model. I ran a dummy simulation just to figure out what I'm doing.
# Run 10,000 sims, work on one simulation at a time (other operations have been mapped to a list of simulation objects)

sim_stpaul <- system.simulate(n.sims = 10000, edges = edges_lim$stpaul, sampler = community.sampler(edges_lim$stpaul), validators = NULL)
sim_stpaul_mod <- sim_stpaul

# Extract row numbers for the edge weights that meet some criterium; for example, I want the row numbers of the weights that are less than 0.7 for the edge "Value of groundfish CDQ -> CBSFA". 
# Could wrap this in a function and map it to list of simulation objects; need to think about how to specify edge names that differ between models (e.g., "Value of groundfish ... [name of CDQ organization]")

# sim$w = matrix of simulated edge weights (i.e., interaction strengths) where columns are edge names, rows are interaction strengths generated by each simulation
# sim$A = list of inverse (i.e., stable) matrices
# sim$total = total number of simulated matrices
# sim$stable = number of stable matrices
# sim$accepted = number of accepted matrices (not sure how this is different than sim$stable)

keep.rows <- which(sim_stpaul_mod$w[,'Value of groundfish CDQ -> CBSFA'] < 0.70)

sim_stpaul_mod$w <- sim_stpaul_mod$w[keep.rows,]

sim_stpaul_mod$A <- sim_stpaul_mod$A[keep.rows]

# Not sure if I should change the number of stable and/or accepted matrices. Maybe just accepted? I don't know whether other functions use those list elements.

# How does modifying the interaction strength of one edge (Value of A80 CDQ -> CBSFA) impact the rest of the model?
# Positive press of Value of A80 CDQ on all other nodes for original and modified simulations

comp_imp <- data.frame(original = pull(as.data.frame(imptable_stpaul), `Value of A80 CDQ`),
                       mod = pull(as.data.frame(imptable_stpaul_mod), `Value of A80 CDQ`)) %>% 
  mutate(pct_diff = (mod-original)/original)

range(comp_imp$pct_diff, na.rm = TRUE)
mean(comp_imp$pct_diff, na.rm = TRUE)

# So, ratcheting the effect of Value of A80 CDQ on CBSFA down by 30% had an essentially negligible effect on the system-wide dynamics.

# On average, the model-wide impact of a positive press on Value of A80 CDQ increased by 1.6% when decreasing the interaction strength of the "Value of A80 CDQ -> CBSFA" edge by 30%.

# Next, median? Basically decrease int strength by 50%. Also didn't change the interaction strength of Value of A80 CDQ in other models or on other nodes; need to decide whether to map over all models and modify all interaction strengths WRT to Value A80 CDQ in the same way

```

```{r Impact tables}
# Create impact tables for each model; values are positive press perturbation of column node impacts (-1 to 1) on row nodes

imptables <- map(.x = sims, .f = impact.table)

# Create heat maps of impact tables

heatimptables <- map(.x = imptables, .f = heatimptable)


# Which node perturbations have similar community outcomes?

imp_dist_pert <- map(.x = imptables, .f = ~ hclust(dist(t(.))))
# plot() args
# plot(imp_dist_pert$stpaul, main = paste(names(.), "Perturbation similarity", sep = " "), hang = -1))


imp_dist_node <- map(.x = imptables, .f = ~ hclust(dist(.)))
# plot() args
# plot(imp_dist_node$stpaul, main = paste(names(.), "Node similarity across perturbations (Euclidean distance)", sep = " "), hang = -1)


```

# Saint Paul
## Digraph

`r render_graph(digraphs$stpaul)`

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Digraph showing relationships (edges) between variables (nodes) for the St. Paul community model.


***
## Community matrix

``` {r out.width = '1000px'} 
adj_images$stpaul
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Representation of the Saint Paul community matrix in which blue cells indicate a negative effect of column node on row node, and orange indicate a positive effect. Diagonals in blue indicate that each node in the system is assumed to be self-limiting.


***
## Press perturbations

``` {r out.width = '1000px'}
impact.barplot2(sims$stpaul, perturb = c("Halibut access" = -1), main = "Decrease access to halibut")

```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Impact barpot of simulated responses to an increase in halibut abundance for St. Paul community model. The proportion of simulated stable (retained) matrices that had a negative response at the node in question is shown in blue, and the proportion of stable matrices in which that node had a positive response is shown in orange.


***
## Impact table

``` {r out.width = '1000px'} 
heatimptables$stpaul
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Mean simulated effect on row variable of positive perturbation of column variable.


***
## Node similarity across perturbations

``` {r out.width = '1000px'} 
plot(imp_dist_node$stpaul, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing node similarity across perturbations (Euclidean distance). The more similarly a pair of nodes responds to a press perturbation of any kind, the closer they will be grouped in the dendrogram.


***
## Perturbation similarity

``` {r out.width = '1000px'} 
plot(imp_dist_pert$stpaul, cex = 0.75, xlab = "", main = "", sub = "")
``` 

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing perturbation similarity (Euclidean distance). The more similarly a pair of nodes affects all other nodes when perturbed (positively?), the closer they will be grouped in the dendrogram. 

***

# Savoonga
## Digraph

`r render_graph(digraphs$savoonga)`

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Digraph showing relationships (edges) between variables (nodes) for the Savoonga community model.


***
## Community matrix

``` {r out.width = '1000px'} 
adj_images$savoonga
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Representation of the Savoonga community matrix in which blue cells indicate a negative effect of column node on row node, and orange indicate a positive effect. Diagonals in blue indicate that each node in the system is assumed to be self-limiting.


***
## Press perturbations

``` {r out.width = '1000px'}
impact.barplot2(sims$savoonga, perturb = c("Access to halibut CDQ" = -1), main = "Decrease access to halibut CDQ")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Impact barpot of simulated responses to an increase in halibut abundance for Savoonga community model. The proportion of simulated stable (retained) matrices that had a negative response at the node in question is shown in blue, and the proportion of stable matrices in which that node had a positive response is shown in orange.


***
## Impact table

``` {r out.width = '1000px'} 
heatimptables$savoonga
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Mean simulated effect on row variable of positive perturbation of column variable.


***
## Node similarity across perturbations

``` {r out.width = '1000px'} 
plot(imp_dist_node$savoonga, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing node similarity across perturbations (Euclidean distance). The more similarly a pair of nodes responds to a press perturbation of any kind, the closer they will be grouped in the dendrogram.


***
## Perturbation similarity

``` {r out.width = '1000px'} 
plot(imp_dist_pert$savoonga, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing perturbation similarity (Euclidean distance). The more similarly a pair of nodes affects all other nodes when perturbed (positively?), the closer they will be grouped in the dendrogram. 


# Unalaska/Dutch Harbor
## Digraph

`r render_graph(digraphs$unalaska)`

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Digraph showing relationships (edges) between variables (nodes) for the Unalaska/Dutch Harbor community model.


***
## Community matrix

``` {r out.width = '1000px'} 
adj_images$unalaska
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Representation of the Unalaska/Dutch Harbor community matrix in which blue cells indicate a negative effect of column node on row node, and orange indicate a positive effect. Diagonals in blue indicate that each node in the system is assumed to be self-limiting.


***
## Press perturbations

``` {r out.width = '1000px'}
impact.barplot2(sims$unalaska, perturb = c("Access to halibut CDQ" = -1), main = "Decrease access to halibut CDQ")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Impact barpot of simulated responses to an increase in halibut abundance for Unalaska/Dutch Harbor community model. The proportion of simulated stable (retained) matrices that had a negative response at the node in question is shown in blue, and the proportion of stable matrices in which that node had a positive response is shown in orange.


***
## Impact table

``` {r out.width = '1000px'} 
heatimptables$unalaska
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Mean simulated effect on row variable of positive perturbation of column variable.


***
## Node similarity across perturbations

``` {r out.width = '1000px'} 
plot(imp_dist_node$unalaska, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing node similarity across perturbations (Euclidean distance). The more similarly a pair of nodes responds to a press perturbation of any kind, the closer they will be grouped in the dendrogram.


***
## Perturbation similarity

``` {r out.width = '1000px'} 
plot(imp_dist_pert$unalaska, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing perturbation similarity (Euclidean distance). The more similarly a pair of nodes affects all other nodes when perturbed (positively?), the closer they will be grouped in the dendrogram. 


# Amendment 80
## Digraph

`r render_graph(digraphs$am80)`

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Digraph showing relationships (edges) between variables (nodes) for the Amendment 80 community model.


***
## Community matrix

``` {r out.width = '1000px'} 
adj_images$am80
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Representation of the Amendment 80 community matrix in which blue cells indicate a negative effect of column node on row node, and orange indicate a positive effect. Diagonals in blue indicate that each node in the system is assumed to be self-limiting.


***
## Press perturbations


``` {r out.width = '1000px'} 
impact.barplot2(sims$am80, perturb = c("Halibut bycatch limits" = -1), main = "Decrease halibut bycatch cap")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Impact barpot of simulated responses to a decrease in halibut bycatch cap for Amendment 80 community model. The proportion of simulated stable (retained) matrices that had a negative response at the node in question is shown in blue, and the proportion of stable matrices in which that node had a positive response is shown in orange.


***
## Impact table

``` {r out.width = '1000px'} 
heatimptables$am80
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Mean simulated effect on row variable of positive perturbation of column variable.


***
## Node similarity across perturbations

``` {r out.width = '1000px'} 
plot(imp_dist_node$am80, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing node similarity across perturbations (Euclidean distance). The more similarly a pair of nodes responds to a press perturbation of any kind, the closer they will be grouped in the dendrogram.


***
## Perturbation similarity

``` {r out.width = '1000px'} 
plot(imp_dist_pert$am80, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing perturbation similarity (Euclidean distance). The more similarly a pair of nodes affects all other nodes when perturbed (positively?), the closer they will be grouped in the dendrogram. 



# Mekoryuk (before)
## Digraph

`r render_graph(digraphs$mekoryuk_b)`

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Digraph showing relationships (edges) between variables (nodes) for the Mekoryuk (before) community model.


***
## Community matrix

``` {r out.width = '1000px'} 
adj_images$mekoryuk_b
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Representation of the Mekoryuk (before) community matrix in which blue cells indicate a negative effect of column node on row node, and orange indicate a positive effect. Diagonals in blue indicate that each node in the system is assumed to be self-limiting.


***
## Press perturbations

``` {r out.width = '1000px'}
impact.barplot2(sims$mekoryuk_b, perturb = c("Halibut access" = -1), main = "Decrease access to halibut")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Impact barpot of simulated responses to an increase in halibut abundance for Mekoryuk (before) community model. The proportion of simulated stable (retained) matrices that had a negative response at the node in question is shown in blue, and the proportion of stable matrices in which that node had a positive response is shown in orange.



***
## Impact table

``` {r out.width = '1000px'} 
heatimptables$mekoryuk_b
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Mean simulated effect on row variable of positive perturbation of column variable.


***
## Node similarity across perturbations

``` {r out.width = '1000px'} 
plot(imp_dist_node$mekoryuk_b, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing node similarity across perturbations (Euclidean distance). The more similarly a pair of nodes responds to a press perturbation of any kind, the closer they will be grouped in the dendrogram.


***
## Perturbation similarity

``` {r out.width = '1000px'} 
plot(imp_dist_pert$mekoryuk_b, cex = 0.75, xlab = "", main = "", sub = "")
```

`r figCount <- incCount(figCount)`
`r I(pasteLabel("Figure", figCount, "", FALSE))`. Dendrogram showing perturbation similarity (Euclidean distance). The more similarly a pair of nodes affects all other nodes when perturbed (positively?), the closer they will be grouped in the dendrogram. 

